---
title: "Test statistical assignment"
author: "Alexey Bessudnov"
date: "22 January 2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Please change the author and date fields above as appropriate. Do not change the output format. Once you have completed the assignment you want to knit your document into a markdown document in the "github_document" format and then commit both the .Rmd and .md files (and all the associated files with graphs) to your private assignment repository on Github.

## Reading data (40 points)

First, we need to read the data into R. For this assignment, I ask you to use data from the youth self-completion questionnaire (completed by children between 10 and 15 years old) from Wave 9 of the Understanding Society. It is one of the files you have downloaded as part of SN6614 from the UK Data Service. To help you find and understand this file you will need the following documents:

1) The Understanding Society Waves 1-9 User Guide: https://www.understandingsociety.ac.uk/sites/default/files/downloads/documentation/mainstage/user-guides/mainstage-user-guide.pdf
2) The youth self-completion questionnaire from Wave 9: https://www.understandingsociety.ac.uk/sites/default/files/downloads/documentation/mainstage/questionnaire/wave-9/w9-gb-youth-self-completion-questionnaire.pdf
3) The codebook for the file: https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/datafile/youth/wave/9


```{r}
library(tidyverse)
# This attaches the tidyverse package. If you get an error here you need to install the package first. 

getwd()

Data <- read_tsv("/Users/helenretzlaff/Documents/Data 3/datan3_2020/data/UKDA-6614-tab/tab/ukhls_w9/i_youth.tab")

#the Data has 2821 observations and 216 variables
```

## Tabulate variables (10 points)

In the survey children were asked the following question: "Do you have a social media profile or account on any sites or apps?". In this assignment we want to explore how the probability of having an account on social media depends on children's age and gender.

Tabulate three variables: children's gender, age (please use derived variables) and having an account on social media.

```{r}

mytable<-table(Data[c("i_sex_dv","i_age_dv","i_ypsocweb")])

ftable(mytable)
```

## Recode variables (10 points)

We want to create a new binary variable for having an account on social media so that 1 means "yes", 0 means "no", and all missing values are coded as NA. We also want to recode gender into a new variable with the values "male" and "female" (this can be a character vector or a factor).

```{r}
Data$soc.account[Data$i_ypsocweb==1]<-1
Data$soc.account[Data$i_ypsocweb==2]<-0
Data$soc.account[Data$i_ypsocweb==-9]<-NA
Data$soc.account<-as.numeric(Data$soc.account)

view(Data$soc.account)
summary(Data$soc.account)

#question: why does the new variable not appear in the "big" Data frame? but it does seem to exist somewhere as the number of variables changes and I can view the column

Data$gender<-NA
Data$gender[Data$i_sex_dv==1]<-"male"
Data$gender[Data$i_sex_dv==2]<-"female"
Data$gender<-as.factor(Data$gender)
view(Data$gender)
summary(Data$gender)

#question: why does the new variable not appear in the "big" Data frame? but it does seem to exist somewhere as the number of variables changes and I can view the column 
```

## Calculate means (10 points)

Produce code that calculates probabilities of having an account on social media (i.e. the mean of your new binary variable produced in the previous problem) by age and gender. 

```{r}
tapply(Data$soc.account,Data$i_age_dv,mean,na.rm=TRUE)
```

```{r}
tapply(Data$soc.account,Data$gender,mean,na.rm=TRUE)

```


## Write short interpretation (10 points)

the probability of having a social media account increases with age. Children at the age of 10 have a social media account only 48% of the time while children at the age of 12 already have one 86% of the time. 
regarding gender, the probability of having a social media account is higher for girls (83%) than for boys (78%). 

## Visualise results (20 points)

Create a statistical graph (only one, but it can be faceted) illustrating your results (i.e. showing how the probability of having an account on social media changes with age and gender). Which type of statistical graph would be most appropriate for this?

```{r}
library(ggplot2)
g<-ggplot(data = Data,aes(x=i_age_dv))
g+geom_bar()+facet_wrap(~soc.account)

# I don´t know how to include the gender variable in the same graph
```


```{r}
g2<-ggplot(data = Data, aes(x=gender))
g2+geom_bar()+facet_wrap(~soc.account)
```
## Conclusion

This is a test formative assignment and the mark will not count towards your final mark. If you cannot answer any of the questions above this is fine -- we are just starting this module! However, please do submit this assignment in any case to make sure that you understand the procedure, that it works correctly and you do not have any problems with summative assignments later.
